\chapter{Technological frameworks}
\label{chap:techFrm}


This chapter provides a description of the technological frameworks used during the development phase of your product. Such technological frameworks should be properly introduced and described from the point of view of their use during the development of this system. The iCrash application is supposed to be deployed over at least 3 different modules: database server, application server and client.


\section{Eclipse}
\label{sec:Eclipse}
Eclipse is an integrated development environment (IDE) used in computer programming, and is the most widely used Java IDE. It contains a base workspace and an extensible plug-in system for customizing the environment. 

\section{Programming language}
\label{sec:Programming language}
Main programming language for this system is Java. It requires pre-installed JDK as well as the following DB systems: MySQL Server, MySQL Workbench.


\section{Vagrant}
\label{sec:Vagrant}
Remote access to the system can be provided with Vagrant, an open-source software product for building and maintaining portable virtual development environments.


\section{JavaFX}
\label{sec:JavaFX}
Software platform for developing desktop application that can be used cross-platform. It is used as a main GUI tool of the system.

\section{SceneBuilder}
\label{sec:SceneBuilder}
Scene Builder is a visual layout tool that lets users quickly design JavaFX
application user interfaces, without coding. Users can drag and drop UI
components to a work area, modify their properties, apply style sheets, and the
FXML code for the layout that they are creating is automatically generated in
the background. The result is an FXML file that can then be combined with a Java
project by binding the UI to logic of the application.




