\chapter{Product information}
%Reducing the spacing from the title
\vspace{-6em}


\section{Identification}
This paper contains user manual for iCrash (v1.0) road crises handling system. The System includes:
\begin{itemize}
\item Client application, that provides GUI for actors of the system.
\item Server application that is a centralized entity that processes requests from the clients, keeps connection with the database and is responsible
for data consistency. The business logic of the whole system is located here.
\item Database server that is a persistent storage for storing messages as a
data.
\end{itemize}
\section{Copyright}
Copyright \textcopyright 2014-2017 University of Luxembourg. 
\newline
All rights reserved. iCrash program and the accompanying materials are made available under the terms of the Eclipse Public License v1.0 which accompanies this distribution, and is available at http://www.eclipse.org/legal/epl-v10.html 
\section{Trademark notices}
"iCrash ", "iCrash client", "iCrash server", "iCrash database" and "iCrash
common" are trademarks of University of Luxembourg. 
\section{Restrictions}
Redistribution and use in source and binary forms, with or without modification, are permitted provided that the following conditions are met:				
\begin{itemize}					 						
\item Redistributions of source code must retain the above copyright notice,
this list of conditions and the following disclaimer.
\item Redistributions in binary form must reproduce the above copyright notice,
this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.
\end{itemize}

\section{Warranties}
There is no warranty at all.\\				
This warranty is not valid if system or hardware requirements are not compatible with this product. This warranty is not valid if any of iCrash parts is manually changed. 
\section{Contractual obligations}
The functionalities provided by iCrash are designed only to provide an educational software for the Software Engineering and Development course. This software is not meant to be used for any other purposes. 

\section{Disclaimers}

\section{Contact}
university@innopolis.ru