\chapter{Introduction}
\label{chap:introduction}

\section{Scope}
This document provides the information that is required to use iCrash  the key
components \\
\newline
This document does not describe details of implementation \\
\newline
This document does not provide information of all use cases, but provides all
necessary information about installation and use the iCrash\\
\newline
This document may
be used with other documents of the iCrash (v1.0) system, as well as with the documents provided by third-party companies to have an overall view and correct understanding of the system, how to use and employ it and its benefits.
\newline
\section{Purpose}
The purpose of this document is to provide basic examples of using iCrash client
module. \\
\newline
This document defines the screenshots of iCrash client module and key terms for
understanding iCrash client module interface and functionalities. \\
\newline
This document is meant to be used along with the system at any point of
time of its employment.
\newline
\section{Intended audience}
Intended audience of the documentation are the system actors who actively
exploit main functionalities of the iCrash(v1.0), including Administrator,
Coordinator and Editor.\\
\newline
System actors are expected to refer to the documentation for assistance
regarding any system usage, error messages resolutions and system
operation-related issues.
\newline
\section{\mysystemname}
TODO

\subsection{Actors \& Functionalities}
Administrator - A person who can add new coordinator in the system and in its
environment or delete an existing one.\\
Editor - A person who works with media and chooses which news should be
published. \\
Coordinator - A person who informs about crises \\
Witness - human that is a witness of an accident 	\\
Victim - human that is a victim of an accident



\subsection{Operating environment}
\begin{itemize}
\item Server Application is the main part of the infrastructure, and is
responsible for overall business logic of the system and consistency of the data and request
handling received from Client Application and Database Server.
\item Client Application provides Graphical User Interface for system actors and
sends requests to process to Server Application.
\item Crash requests are processed by the Server Application and corresponding
crash report data is then stored in Database Server. 
\end{itemize}
\section{Document structure} 
TODO 
Information on how this document is organised and it is expected to be
used. Recommendations on which members of the audience
should consult which sections of the document, and explanations about the used
notation (i.e. description of formats and conventions) must also be provided.





